---
title: "COVID19 in Qatar"
description: |
  Exploring the impact of COVID19 in Qatar
author:
  - name: Ibrahim Al-Hindi
date: 08-26-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(tidycovid19)
library(table1)
library(DT)
```


```{r data}
#covid_data <- download_jhu_csse_covid19_data(cached = TRUE)

#write_csv(covid_data, "../../data/covid_data.csv")

data <- read_csv("../../data/covid_data.csv")

qatar <- data %>%
  filter(country == "Qatar",
         date < "2021-08-05") %>%
  select(-timestamp)

qatar_1 <- qatar %>%
  mutate(daily_confirmed = c(0, diff(confirmed)),
         daily_deaths = c(0, diff(deaths)),
         daily_recovered = c(0, diff(recovered))) %>%
  select(country, iso3c, date, daily_confirmed, confirmed, daily_deaths, deaths, daily_recovered, recovered) %>%
  rename(acc_confirmed = confirmed,
         acc_deaths = deaths,
         acc_recovered = recovered)

```


# Data Description

The data is sourced from the **tidycovid19** R package created by **Joachim Gassen** on [Github](https://github.com/joachim-gassen/tidycovid19), which in turn sourced the data from **The Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE)** publicly available [Github repository](https://github.com/CSSEGISandData/COVID-19). JHU CSSE collated the numbers from the responsible body of each country.

The data contains the following variables:

|**variable**      |**class** |**description** |
|:-----------------|:---------|:-----------|
|country           |character |Country name |
|iso3c             |character | ISO3c country code as defined by ISO 3166-1 alpha-3 |
|date              |date      | Calendar date |
|daily_confirmed   |numeric   | Daily increase in Covid-19 cases |
|acc_confirmed     |numeric   | Accumulated Covid-19 cases |
|daily_deaths      |numeric   | Daily increase in Covid-19 deaths |
|acc_deaths        |numeric   | Accumulated Covid-19 deaths |
|daily_recovered   |numeric   | Daily increase in Covid-19 recoveries |
|acc_recovered     |numeric   | Accumulated Covid-19 recoveries |


# Summary Table

```{r}
table1(~daily_confirmed + acc_confirmed + daily_deaths + acc_deaths + daily_recovered + acc_recovered,
       data = qatar_1,
       caption = )
```
<br>

What can be noticed from the table is the extremely low number of total deaths at `r max(qatar_1$acc_deaths)` from a total of `r format(plyr::round_any(max(qatar_1$acc_confirmed), 1000, ceiling), scientific = FALSE, big.mark = ",")` cases, representing a death rate of only **`r round(max(qatar_1$acc_deaths)/plyr::round_any(max(qatar_1$acc_confirmed), 1000, ceiling) * 100, 2)`%**, which is extremely low compared to the global average of 2% (World Health Organisation [WHO], 2021). Several factors contributed to this figure. One of which is that Qatar has a relatively low median age at 32.3 years (Worldometer, 2021). Additionally, a fine of up to $53,000 has been instated for anyone who does not wear a face covering in public, and as per a Qatari official "anyone who tests positive for coronavirus immediately receives high-quality medical treatment at no cost" (Tadros, 2020).






```{r}
datatable(qatar_1, options = list(pageLength = 10))
```



# References

- Tadros, A. (2020, May 15). Coronavirus spreads "exponentially" in Qatar's labor camps. *CBS News*. Retrieved from https://www.cbsnews.com/news/coronavirus-in-qatar-spreads-exponentially-in-migrant-worker-labor-camps/

- World Health Organisation (2021). *WHO Coronavirus (COVID-19) Dashboard*. Retrieved from https://covid19.who.int/

- Worldometer (2021). *Qatar Population*. Retrieved from https://www.worldometers.info/world-population/qatar-population/






























