---
title: "COVID19 in Qatar"
description: |
  Communicating the impact of COVID19 in Qatar
author:
  - name: Ibrahim Al-Hindi
date: 08-26-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(tidycovid19)

```


```{r data}
qatar <- download_jhu_csse_covid19_data(cached = TRUE)

qatar <- qatar %>% 
  filter(country == "Qatar") %>% 
  select(-timestamp)

td <- tidycovid19_data_sources
```


# Data Description

The data is sourced from the **tidycovid19** R package created by **Joachim Gassen** on [Github](https://github.com/joachim-gassen/tidycovid19), which in turn sourced the data from **The Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE)** publicly available [Github repository](https://github.com/CSSEGISandData/COVID-19). JHU CSSE collated the numbers from the responsible body of each country.

The data contains the following variables:

|**variable**|**class** |**description** |
|:---------- |:---------|:-----------|
|country     |character |Country name |
|iso3c       |character | ISO3c country code as defined by ISO 3166-1 alpha-3 |
|date        |date      | Calendar date |
|confirmed   |numeric   | Covid-19 cases (accumulated) |
|deaths      |numeric   | Covid-19 deaths (accumulated) |
|recovered   |numeric   | Covid-19 recoveries (accumulated)|







































